An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps

### 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
use filter dist for individual centroids

```{r close_points}
# filter grid for avaiable points
centroid1 <- centroids %>% head(1)

@@

hex_grid <- hex_grid %>% ungroup() %>%
        filter(flat - buffer_dist < hex_lat & hex_lat < flat + buffer_dist) %>%
        filter(flong - buffer_dist < hex_long & hex_long < flong + buffer_dist)

@@

        hex_grid <- hex_grid %>%
            # create circle of radius: hex_filter
            filter(hyp < hex_filter) %>%
            mutate(
                # geosphere takes a long time
                angle = f_angle,
                angle_plus = (angle + width)%%360,
                angle_minus = (angle - width)%%360,
                atan = atan2(hex_lat_c, hex_long_c),
                hex_angle = (atan*180/pi),
                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))

>>>>

```{r close_points}
filter_dist <- hex_filter*hex_size

# filter grid for avaiable points
centroid1 <- centroids %>% head(1)

@@

hex_grid <- hex_grid %>% ungroup() %>%
        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)

@@

        hex_grid <- hex_grid %>%
            # create circle of radius: hex_filter
            filter(hyp < filter_dist) %>%
            mutate(
                # geosphere takes a long time
                angle = f_angle,
                angle_plus = (angle + width)%%360,
                angle_minus = (angle - width)%%360,
                atan = atan2(hex_lat_c, hex_long_c),
                hex_angle = (atan*180/pi),
                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))
